Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-04-01 paper.tex
new abstract and conclusion ... imaginary boat scene

\begin{abstract} 
\todo{We encourage industrial and academic users of constraint technology to submit papers on completed or on-going practical projects. Papers comparing constraint technology to other optimization techniques (MIP, local search, SAT, etc.) on a realistic application with a sound experimental evaluation are also encouraged. Papers which clearly define users' benefits, describe the required effort to build the application and the time frame in which it was delivered, will match the acceptance criteria most closely. The novelty of the application domain, while potentially a plus, is not the only deciding acceptance criterion. Application papers will be reviewed by a program committee with significant experience in the use of CP in applications. The writing of the paper should be guided by providing answers to four main questions: Problem being solved? Why CP? How CP? Added value of CP? Formatting, length, and dates for submissions are the same as for the technical track.}
\end{abstract}

@@

>>>>

\begin{abstract} 
We present a constraint programming solution to the problem of generating round-robin schedules for dinghy sailing match races. Our schedules satisfy the widely used ISAF World Sailing pairing lists match race criteria. We show that some published ISAF schedules are in fact illegal, and present corresponding legal instances and schedules that have not previously been published. Our schedules can be downloaded as blanks, then populated with actual competitors and used in ISAF competitions. 
\end{abstract}

@@

\begin{center}
\begin{figure}[tb]
\hspace{-1cm}
\includegraphics[height=12cm,width=17.5cm]{dinghy.jpg}
\vspace{-30mm}
\caption{Scene from an imaginary dinghy race.}
\label{dinghy}
\end{figure}
\end{center}
